A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-02 sections/Overview.tex
local changes

In recent work, \citet{itp2018} have shown how to mechanise a variant of DK's
subtyping algorithm and shown it correct with respect to DK's declarative
subtyping judgment. This approach overcomes the problem's in DK's formulation
by using a \emph{worklist}-based judgment of the form $$\Gamma \vdash \Omega$$
where $\Omega$ is a worklist (or sequence) of subtyping problems of the
form $A \leq B$.  The judgment is defined by case analysis on the first
element of $\Omega$ and recursively processes the worklist until it is empty.
Using both a single common ordered context $\Gamma$ and a worklist $\Omega$ greatly
simplifies propagating the instantiation of type variables in one
subtyping problem to the remaining ones.

@@

\paragraph{No Inference Judgments} 
Secondly and more importantly, the approach only deals with a judgment for
\emph{checking} whether one type is the subtype of another. While this may not
be so difficult to adapt to the \emph{checking} mode of term typing $\Gamma
\vdash e \Leftarrow A$, it clearly lacks the functionality to support the
\emph{inference} mode of term typing $\Gamma \vdash e \Rightarrow A$. Indeed,
the latter requires not only the communication of unification variable
instantiations from one typing problem to another, but also an inferred type.

>>>>

In recent work, \citet{itp2018} have shown how to mechanise a variant of DK's
subtyping algorithm and shown it correct with respect to DK's declarative
subtyping judgment. This approach overcomes the some problems in DK's formulation
by using a \emph{worklist}-based judgment of the form $$\Gamma \vdash \Omega$$
where $\Omega$ is a worklist (or sequence) of subtyping problems of the
form $A \leq B$.  The judgment is defined by case analysis on the first
element of $\Omega$ and recursively processes the worklist until it is empty.
Using both a single common ordered context $\Gamma$ and a worklist $\Omega$ greatly
simplifies propagating the instantiation of type variables in one
subtyping problem to the remaining ones.

@@

\paragraph{No Inference Judgments} 
Secondly, and more importantly, the approach only deals with a judgment for
\emph{checking} whether one type is the subtype of another. While this may not
be so difficult to adapt to the \emph{checking} mode of term typing $\Gamma
\vdash e \Leftarrow A$, it clearly lacks the functionality to support the
\emph{inference} mode of term typing $\Gamma \vdash e \Rightarrow A$. Indeed,
the latter requires not only the communication of unification variable
instantiations from one typing problem to another, but also an inferred type.
